PACE Solver Description: OCMu64,\\ a solver for One-sided Crossing Minimization

### 2024-09-20 tex/paper.tex
update title
Reference lemma/observation in figure caption

\title{OCMu64: a solver for One-sided Crossing Minimization} %TODO Please add

@@

\begin{figure}[t]
\centering
\hfill
\subfloat[An instance of \cref{lem:weak}.]{
\includegraphics[width=0.30\textwidth]{fig/simple.pdf}%
\label{fig:simple}
}
\hfill
\subfloat[Examples of blocking sets in blue.]{
\includegraphics[width=0.6\textwidth]{fig/blocking-set.pdf}%
\label{fig:blocking-set}
}
\hfill
\\
\subfloat[Examples of strongly fixed pairs.]{
\includegraphics[width=0.9\textwidth]{fig/strongly-fixed.pdf}%
\label{fig:strongly-fixed}
}
%% \subfloat[]{
%% \includegraphics[width=0.33\textwidth]{fig/gluing.pdf}%
%% \label{fig:gluing}
%% }
\caption{
  Various examples where $u\b v$, where $u,v\in B$ can freely move around and
  their neighbours in $A$ (on the dashed line) have fixed positions.}%
\label{fig}
\end{figure}

@@

\begin{definition}[Strongly fixed pair]
    We call $u, v \in B$ a \emph{strongly fixed pair} if for every $b \in A$ we have ${\sum_{a
    \leq b} \bar u(a) \geq \sum_{a \leq b} \bar v(a)}$, and at least one of these inequalities
    is strict. Note that this implies $r(u, v) < 0$.
\end{definition}
\begin{lemma}\label{lem:sfp} When $u, v$ is a strongly fixed pair,
    then for any $w: A\to \mathbb R^{\geq 0}$ we have 
    \[
        r(w, \bar v) \leq r(w, \bar u).
    \]
\end{lemma}
\begin{proof}
    Consider the least element $a_0 \in A$ such that $\bar u(a_0) \neq
    \bar v(a_0)$. We must have $\bar u(a_0) > \bar v(a_0)$. Now consider the transformation of
    $\bar u$ which ``moves'' $\delta := \bar u(a_0) - \bar v(a_0)$ of weight from $a_0$ to its
    successor $a_1 \in A$, and call this transformed function $\bar u'$. Then
    \[
        r(w, \bar u') = r(w, \bar u) - \delta w(a_0) - \delta w(a_1) \leq r(w, \bar u).
    \]
    Since $\bar v$ is obtained from $\bar u$ by a sequence of such transformations,
    the inequality follows.
\end{proof}
\begin{lemma}\label{lem:sfimplf}
    If $(u, v)$ is strongly fixed, then $u \b v$.
\end{lemma}
\begin{proof}
    Suppose towards a contradiction that $v < x_0 < \cdots < x_k < u$ is part of an optimal
    solution. Write $X = \sum_i x_i$ for the combined function. Then by assumption $r(X, u)
    \leq 0$, and therefore $r(X, v) = W_v r(X, \bar v) \leq W_v r(X, \bar u) = W_v / W_u \cdot
    r(X, u) \leq 0$. But then $c(X, u, v) < c(X, v, u)\leq c(v, X, u)$, which
    contradicts $(v,X,u)$ being optimal.
\end{proof}

>>>>

\title{PACE Solver Description: OCMu64,\\ a solver for One-sided Crossing Minimization} %TODO Please add

@@

\begin{figure}[t]
\centering
\hfill
\subfloat[An instance of \cref{lem:weak}.]{
\includegraphics[width=0.30\textwidth]{fig/simple.pdf}%
\label{fig:simple}
}
\hfill
\subfloat[Examples of blocking sets (\cref{pfp}) in blue.]{
\includegraphics[width=0.6\textwidth]{fig/blocking-set.pdf}%
\label{fig:blocking}
}
\hfill
\\
\subfloat[Examples of strongly fixed pairs (\cref{def:sfp}).]{
\includegraphics[width=0.9\textwidth]{fig/strongly-fixed.pdf}%
\label{fig:strongly-fixed}
}
%% \subfloat[]{
%% \includegraphics[width=0.33\textwidth]{fig/gluing.pdf}%
%% \label{fig:gluing}
%% }
\caption{
  Various examples where $u\b v$, where $u,v\in B$ can freely move around and
  their neighbours in $A$ (on the dashed line) have fixed positions.}%
\label{fig}
\end{figure}

@@

\begin{definition}[Strongly fixed pair]\label{def:sfp}
    We call $u, v \in B$ a \emph{strongly fixed pair} if for every $b \in A$ we have ${\sum_{a
    \leq b} \bar u(a) \geq \sum_{a \leq b} \bar v(a)}$, and at least one of these inequalities
    is strict. Note that this implies $r(u, v) < 0$.
\end{definition}
\begin{lemma}\label{lem:sfp} When $u, v$ is a strongly fixed pair,
    then for any $w: A\to \mathbb R^{\geq 0}$ we have 
    \[
        r(w, \bar v) \leq r(w, \bar u).
    \]
\end{lemma}
\begin{proof}
    Consider the least element $a_0 \in A$ such that $\bar u(a_0) \neq
    \bar v(a_0)$. We must have $\bar u(a_0) > \bar v(a_0)$. Now consider the transformation of
    $\bar u$ which ``moves'' $\delta := \bar u(a_0) - \bar v(a_0)$ of weight from $a_0$ to its
    successor $a_1 \in A$, and call this transformed function $\bar u'$. Then
    \[
        r(w, \bar u') = r(w, \bar u) - \delta w(a_0) - \delta w(a_1) \leq r(w, \bar u).
    \]
    Since $\bar v$ is obtained from $\bar u$ by a sequence of such transformations,
    the inequality follows.
\end{proof}
\begin{lemma}\label{lem:sfimplf}
    If $(u, v)$ is strongly fixed, then $u \b v$.
\end{lemma}
\begin{proof}
    Suppose towards a contradiction that $v < x_0 < \cdots < x_k < u$ is part of an optimal
    solution. Write $X = \sum_i x_i$ for the combined function. Then by assumption $r(X, u)
    \leq 0$, and therefore $r(X, v) = W_v r(X, \bar v) \leq W_v r(X, \bar u) = W_v / W_u \cdot
    r(X, u) \leq 0$. But then $c(X, u, v) < c(X, v, u)\leq c(v, X, u)$, which
    contradicts $(v,X,u)$ being optimal.
\end{proof}
